Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-24 DGMM2025/paper.tex
Working on 4

    \paragraph*{Application to curvature estimation.}
    Then, to compute the curvatures, we use the Corrected Normal
    Current estimator~\cite{lachaud:2022-dcg} which are based on the
    normals computed above.

>>>>

    \paragraph*{Application to curvature estimation.}
    In order to illustrate better that the visibility normals better
    take into account the sharp features of a digital surface while
    staying meaningfull in digitization of smooth parts, we compare
    the curvature estimates induced by different discrete normal
    estimators. We exploit the \emph{Corrected Normal Current (CNC)
    estimator}, whose theory is detailed in \cite{lachaud:2022-dcg}
    and which can estimate all kinds of curvatures given positions and
    normals. It produces state-of-the-art curvature estimates on
    polygonal surfaces \cite{lachaud:2020-cgf}, point clouds
    \cite{lachaud:2023-cgf}, and even outperforms Integral Invariant
    curvature estimates \cite{coeurjolly:2014-cviu} on digital
    surfaces \cite{lachaud:2022-dcg}. Its implementation is also
    available in
    \href{https://dgtal-team.github.io/doc-nightly/moduleCurvatureMeasures.html}{\textsc{DGtal}}.

    Then,
    to compute the curvatures, we use the Corrected Normal Current
    estimator~\cite{lachaud:2022-dcg} which are based on the normals
    computed above.
